%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Developer CV
% LaTeX Template
% Version 1.0 (28/1/19)
%
% This template originates from:
% http://www.LaTeXTemplates.com
%
% Authors:
% Jan Vorisek (jan@vorisek.me)
% Based on a template by Jan Küster (info@jankuester.com)
% Modified for LaTeX Templates by Vel (vel@LaTeXTemplates.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{developercv} % Default font size, values from 8-12pt are recommended
\usepackage{enumitem}
%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Abi}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Hunter}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Software Engineer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{11}{Chicago}\\
	\icon{Phone}{11}{+1 505 414 2360}\\
	\icon{At}{11}{\href{mailto:abihunter@gmail.com}{abihunter@gmail.com}}\\	
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Globe}{11}{\href{https://westminsterabi.github.io/}{westminsterabi.github.io}}\\
	\icon{Github}{11}{\href{https://github.com/westminsterabi}{@westminsterabi}}\\
	\icon{Twitter}{11}{\href{https://twitter.com/@abi__hunter}{@abi\_\_hunter}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

\cvsect{Who Am I?}

\begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	I'm a recent Master's graduate in computer science and a Bachelor's graduate in linguistics at the University of Chicago. I have professional experience in backend, frontend, and mobile development. I have also taken masters classes in functional programming, iOS development, and application security. Some of my favorite things are: generative semantics and syntax, systems programming, and Star Trek.% Dummy text
\end{minipage}
\hfill % Whitespace between
\begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\begin{barchart}{5.5}
		\baritem{JavaScript}{60}
		\baritem{Python}{90}
		\baritem{Haskell}{50}
		\baritem{Swift}{40}
		\baritem{C++}{50}
		\baritem{Go}{30}
	\end{barchart}
\end{minipage}

\begin{center}
	\bubbles{6/JetBrains, 5/XCode, 4/vim, 4/Google Cloud, 6/git }
\end{center}

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{2017 -- Present}
		{Software Engineering Intern}
		{The Tuesday Company}
		{Full stack development intern working on feature development including: a react native application for Android and iOS, a react.js dashboard for content management, setup and migration of a MySQL database, and creation of a flask api. \\ \texttt{React Native}\slashsep\texttt{flask}\slashsep\texttt{MySQL}}
	\entry
		{2018 -- Present}
		{Teaching Assistant}
		{University of Chicago Computer Science Department}
		{Teaching assistant for CMSC 121--123 Computer Science With Applications. Topics covered include: Python programming, basic C programming, introduction to big data, multithreading in C, Linux command line. Duties included responding to student questions on online forum, running office hours, and assisting students with code labs.\\ \texttt{C}\slashsep\texttt{Python}\slashsep\texttt{Django}\slashsep\texttt{Linux}}
	
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2018 -- 2019}
		{Master of Science, Computer Science}
		{University of Chicago}
		{Professionally-oriented masters program in computer science, with core requirements in systems, algorithms, and discrete mathematics. Electives taken include iOS Development, Application Security, and C++ for Advanced Programmers}
	\entry
		{2015 -- 2019}
		{Bachelor of Arts, Linguistics}
		{University of Chicago}
		{Comprehensive liberal arts education with thirteen-course concentration in linguistics. Particular focus on semantics and syntax. Year abroad at University College London.` \\ BA Thesis: ``Something fits here, but I don't know what'': an analysis of the hybrid identity condition on sluicing. Awarded departmental honors.}

\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages

	\cvsect{Languages}
	
	\textbf{English} - native\\
	\textbf{French} - fluent\\
	\textbf{Icelandic} - A2\\
	\textbf{Hebrew} - A2 \\
	\textbf{Mandarin} - A1 \\
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	\cvsect{Awards}
	\begin{itemize}[noitemsep, topsep=0pt]
	\item Dean's list, 2015-16
	\item Dean's list, 2016-17
	\item BA Honors, Department of Linguistics
	\end{itemize}
\end{minipage}
\hfill
\begin{minipage}[t]{0.3\textwidth}
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	\cvsect{Hobbies}
	
	I love knitting, drawing, and writing. I won 3rd place in the University of Chicago Study Abroad Office's writing contest in 2018. 
\end{minipage}
\hfill
\begin{minipage}[t]{0.5\textwidth}
	%\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	%\cvsect{Misc Skills}
	
	
\end{minipage}

%----------------------------------------------------------------------------------------

\end{document}
